### 2015-02-20 fundamentals/impl.tex
simpler words for simple minds (like katys).

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{Gidden2014}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, LPs solve much faster than
\gls{MILP}s. However, the capability to model both exists in \Cyclus in order to
provide users with the desired level of fidelity.

@@

The \gls{DRE} is a novel simulation concept in the nuclear fuel cycle domain. It
provides a flexible supply-demand infrastructure, supporting dynamic flows of
resources between agents. Trading between agents can be affected by both the
proposed quality of a resource and agent relationships through the use of
cardinal preferences. Accordingly, a wide range of possible effects can be
modeled, from capacitated fuel supply to international trade agreements.

>>>>

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{Gidden2014}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, LPs solve much faster than
\gls{MILP}s. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.

@@

The \gls{DRE} is a novel simulation concept in the nuclear fuel cycle domain. It
provides a flexible supply-demand infrastructure, supporting dynamic flows of
resources between agents. Trading between agents can be affected by both the
proposed quality of a resource and agent relationships through the use of
preferences. Accordingly, a wide range of possible effects can be
modeled, from capacitaty-limited fuel supply to international trade agreements.
